NTM CT Scoring - Initial Agreement

### 2023-04-04 Stacey Martiniano/ntm_agreement.qmd
Update ntm_agreement.qmd
random effects approach

```{r}
# Agresti examples
agt = matrix(c(22,2,2,0,
               5,7,14,0,
               0,2,36,0,
               0,1,17,10),
             byrow = T,ncol = 4)
dimnames(agt) = list("A"=1:4,"B"=1:4)
# As vectors
c1 = rep(1:4,times=diag(agt))
c1 = c(c1,rep(1:4,times=rowSums(agt*lower.tri(agt))))
c1 = c(c1,rep(1:4,times=rowSums(agt*upper.tri(agt))))
c2 = rep(1:4,times=diag(agt))
c2 = c(c2,rep(1:4,times=colSums(agt*lower.tri(agt))))
c2 = c(c2,rep(1:4,times=colSums(agt*upper.tri(agt))))
# Check
table(c1,c2)
# Data from Agresti Biometrics 1988
agt=matrix(c(1,1,22,1,2,2,1,3,2,1,4,0,1,5,0,
2,1,5,2,2,7,2,3,14,2,4,0,2,5,0,
3,1,0,3,2,2,3,3,36,3,4,0,3,5,0,
4,1,0,4,2,1,4,3,14,4,4,7,4,5,0,
5,1,0,5,2,0,5,3,3,5,4,0,5,5,3),byrow = T,ncol = 3)
```

@@

>>>>

@@

# Bootstrap

To calculate bootstrap CIs for an kappa, we generated 1000 bootstrap samples clustered by scan ID and location, and calculated Fleiss' $\kappa$ for each bootstrap sample. Percentile and bias-corrected and accelerated (BCa) intervals are presented below.

```{r}
library(boot)
boot_fleiss <- function(df, i) {
  d <- df[i,c("AF","DL","JW")] # allows boot to select sample
  k = kappam.fleiss(d)
  return(k$value)
}
```

```{r}
# Remove scans and features with no variability
df_list = split.data.frame(data,f = ~ scan_id + feature)
perfect_agreement = lapply(df_list,function(d){
  if(all(d$disagree==FALSE) | all(d$disagree==TRUE)){
    return(names(d))
  } else {
    return(NA)
  }
})
boot_df = data
```

## Kappa

### Overall

```{r}
ka <- boot(data,boot_fleiss,R=1000,strata = interaction(factor(data$scan_id),factor(data$location)))
ci=boot.ci(ka,type = c("perc","bca"))
```

Fleiss' $\kappa$ across all features was `r round(ci$t0,3)` (percentile CI: `r paste(round(ci$percent[4],3),"-",round(ci$percent[5],3))`, BCa CI: `r paste(round(ci$bca[4],3),"-",round(ci$bca[5],3))`)

## Tetra/polychoric correlation

```{r}

```

## Random effects

In this scenario we have multiple crossed random effects. Each scan contains every level of feature and region, and each level of feature contains each level of region (or vice versa).

```{r}
library(lme4)
library(performance)
# Long data for lmer
re_data_no_bronch = data %>% select(-disagree) %>% 
  filter(feature != "Bronchiectasis") %>% # Remove bronchiectasis because it's on a different scale?
  pivot_longer(AF:JW)
re_data_no_bronch$value = factor(as.character(re_data_no_bronch$value),levels = c("Unchecked", "Checked"))
# Logistic model
m = glmer(value~name+(1|scan_id)+(1|feature)+(1|location),
         data = re_data_no_bronch,family="binomial")
summary(m)
# Logistic model
m2 = glmer(value~name+(1|scan_id)+(1|feature),
         data = re_data_no_bronch,family="binomial")
summary(m2)
icc(m2)
icc(m2,by_group = T)
```

There is essentially no variability in the random effect for location (which I think is good?).
